### 2014-06-03 ACL2014/experiments.tex
updating experiment section

\section{Experiments}
In this section, we illustrate experimental results to evaluate our distributed neighbor search framework.
Our experiments are conducted on publicly available query logs collected from the AOL search engine~\cite{Pass06} as well as a 
large-scale query log from a commercial search engine.

\begin{table}
\centering
\begin{tabular}{|c|r|r|}
\hline
Data & $N$ & $D$  \\ 
\hline
\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
\hline 
 \end{tabular}
\caption{\footnotesize{Query-logs statistics}}
\label{tab:data}
\end{table}

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, we perform evaluations using a large query log 
from a commercial search engine, denoted as Qlogs. 
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion).   
Specifically, each dimension in the feature vector of a query $q$ corresponds to a webpage (urls) that have received a user click for $q$. The weight of 
an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  
As a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

\paragraph{Test Data}: We conduct all the experiments using $2000$ random queries sampled from the query logs as the test set of queries. 
For evaluation, we compute the true similar candidates for all the $2000$ test queries by calculating cosine similarity 
between each test query and all the queries in the rest of the dataset. For most of the experiments, we set the similarity threshold  $\tau=0.7$, 
meaning that the algorithm needs to retrieve candidates that have cosine similarity larger than or equal to $0.7$.

\subsection{Evaluation Metrics}
We use two metrics for evaluation: recall and number of comparisons. 
Recall of an LSH algorithm is the fraction of \emph{true} similar candidates (found using candidates returned by computing exact cosine similarity) 
that is retrieved by the LSH algorithm.  
The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
The goal of this paper is to maximize recall and minimize the number of comparisons.

>>>>

\def\qvec{\textbf{q}}
\section{Experiments}
In this section, we illustrate experimental results to evaluate our distributed neighbor search framework.
Our experiments are conducted on publicly available query logs collected from the AOL search engine~\cite{Pass06} as well as a 
large-scale query log from a commercial search engine.

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Data & $N$ & $D$  \\ 
\hline
\aol &  $0.3 \times 10^6$  & $0.7 \times 10^6$ \\
\dataA & $6 \times 10^6$  & $66 \times 10^6$ \\
\dataB & $62 \times 10^6$  & $464 \times 10^6$ \\
\dataC &  $617 \times 10^6$  & $ 2.4 \times 10^9$  \\
\hline 
 \end{tabular}
\caption{\footnotesize{Query-logs statistics}}
\label{tab:data}
\end{table}

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, a large query log 
from a commercial search engine, denoted as Qlogs, is used for evaluations.
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query $q$, a feature vector in a high dimensional feature space is defined as
$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$.
%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion). Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$. The weight of an url for $q$ is defined as the click through rate of the url.  
Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

\paragraph{Test Data} All the experiments are performed using queries $Q$ randomly sampled from the query logs as the test set of $2000$ queries. 
That is, we want to find set $T$, where $T~=~\{~l~\mid~s(q, q')~\geq~\tau~\}$, $s(q, q')$ is a cosine similiarty, and $q' \in \{\dataA, \dataB, \dataC\}$. 
%For evaluation, we compute the true similar cafor all the $2000$ test queries by calculating cosine similarity 
%between each test query and all the queries in the rest of the dataset. 
For most of the experiments, we set the similarity threshold  $\tau=0.7$.
%meaning that for $q$, candidates $q'$ having  cosine similarity of larger than or equal to $0.7$ are retrieved.

\paragraph{Evaluation Metrics}
We use two metrics for evaluation: recall and number of comparisons. 
Recall of an LSH algorithm is the fraction of \emph{true} similar candidates (found using candidates returned by computing exact cosine similarity) 
that is retrieved by the LSH algorithm.  
The number of comparisons performed by an algorithm is computed as the average number of pairwise comparisons that is done per test query. 
The goal of this paper is to maximize recall and minimize the number of comparisons.
